Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-11-10 prop_letter.tex
prop_letter.tex \newcommand{\muB}{\ensuremath{\mu^{B}}} Defined to satisfy the different requirement for different journals...

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{framed}
\newcommand{\amr}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}\end{framed}}
\newcommand{\yutsung}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}\end{framed}}
\newcommand{\gerardo}[1]{\fbox{\begin{minipage}{0.9\linewidth}\color{OliveGreen}{Gerardo says: #1}\end{minipage}}}
\newcommand{\andy}[1]{\fbox{\begin{minipage}{0.9\linewidth}\color{blue}{Andy says: #1}\end{minipage}}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}\mathrel{}\middle|\mathrel{}{#2}\right\} }}
\newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
\allowdisplaybreaks
\newcommand{\coreBorn}{\ensuremath{\overline{\Hilb}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
\setcounter{secnumdepth}{3}
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\rmd}{\mathrm{d}}
\newcommand{\rmi}{\mathrm{i}}
\lineskiplimit=1pt
\newcommand{\ultramodular}{\mathcal{M}}
\newcommand{\ultramodularL}[1][]{\ensuremath{\ultramodular^{\mathrm{L{#1}}}}}
\newcommand{\ultramodularR}[1][]{\ensuremath{\ultramodular^{\mathrm{R{#1}}}}}

@@

A conventional quantum probability measure can easily be constructed
using the Born rule if one knows the current state of the quantum
system.  Specifically, for each pure normalized quantum
state~$\ket{\phi} \in {\cal H}$, the Born rule induces a probability measure
$\mu_{\phi}^{\mathrm{B}}$ defined as
$\mu_{\phi}^{\mathrm{B}}(P)=\melem{\phi}{P}{\phi}$. The situation
generalizes to mixed states
$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, $\ket{\phi_j} \in {\cal H}$, where $q_j > 0$ and
$\sum_{j=1}^{N}q_{j}=1$, in which case the generalized Born rule
induces a probability measure $\mu_{\rho}^{\mathrm{B}}$ defined as
$\mu_{\rho}^{\mathrm{B}}\left(P\right) = \Tr\left(\rho P\right) =
\sum_{j=1}^{N}
q_{j}\mu_{\phi_{j}}^{\mathrm{B}}\left(P\right)$~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.

@@

In the remainder of this section, we will show that our definition of
QIVPMs is consistent with classical IVPMs in the sense that a
restriction of QIVPMs to commuting events recovers the definition of
classical IVPMs. To formalize this connection between QIVPMs and
classical IVPMs, we first note that in contrast to the case with
conventional quantum probability spaces, there is generally no unique
state~$\rho$ consistent with a QIVPM. We say that a QIVPM $\bar{\mu}$
is consistent with a state $\rho$ and projector~$P$ if the interval
$\bar{\mu}(P)$ contains the exact probability calculated by the Born
rule, i.e, if:
\begin{equation}
\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)
\end{equation}
where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
is the probability of the event~$P$ as determined by the Born
rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.

We generalize this consistency relation to sets of states and general
subspaces of events as follows. A set of events $\events'$ is a
\emph{subspace} of $\events$ if it contains $\mathbb{0}$
and~$\mathbb{1}$ and is closed under complements, sums, and products,
i.e., for any projector~$P\in\events'$, we have
$\mathbb{1}-P\in\events'$ and for each pair of commuting
projectors~$P_{0}\in\events'$ and $P_{1}\in\events'$, we have
$P_{0}+P_{1}-P_{0}P_{1}$ and $P_{0}P_{1}\in\events'$. Given a
probability measure $\bar{\mu}$ and a subspace of events $\events'$,
we denote the collection of all states that are consistent with
$\bar{\mu}$ on every projector in $\events'$ as
$\coreBorn(\bar{\mu},\events')$:
\begin{equation}
\label{eq:hbar}
\coreBorn\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in \events',~\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}.
\end{equation}

@@

\begin{definition}[Expectation Value of Observables over QIVPMs] Let
  $\mathscr{I}$ be a set of intervals; $\Hilb$ a Hilbert space of
  dimension $d$ with event space~$\events$; and $\mathbf{O}$ an
  observable with spectral decomposition
  $\Sigma_{i=1}^d \lambda_iP_i$. Let $\events'$ be the minimal
  subspace of events containing all the projectors $P_i$ in the
  spectral decomposition of $\mathbf{O}$ and define:
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}
\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}
\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}\right]\,. \label{eq:quantum-interval-expectation-core}
\end{equation}
\end{definition}

\noindent Intuitively the expectation value of an observable relative
to a QIVPM $\bar{\mu}$ lies between two possible outcomes, which
themselves lie between the minimum and maximum bounds of the
probability intervals associated with each state~$\rho$ that is
consistent with~$\bar{\mu}$ on every projector in the spectral
decomposition of the observable. If $\bar{\mu}$ is a conventional
(Born) probability measure induced by a state $\rho$, then the Born
rule probability induced by every state in
$\coreBorn\left(\bar{\mu},\events'\right)$ will be
$\mu_{\rho}^{\mathrm{B}}$ and the interval collapses to a point, thus
reducing the definition to that of
Eq.~(\ref{eq:quantum-expectation})~\citep{HOSTunpublished}.
% For example, we can extend one of the fragments of valid probability
% measures~$\mu_{1}$ defined in Table~\ref{tab:quantum-probability-measure}
% to a QIVPM~$\bar{\mu}_{3}$:
% \begin{equation}
% \begin{aligned}\bar{\mu}_{3}(\proj{0}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] & \bar{\mu}_{3}(\proj{2}) & =\left[0,0\right]\\
% \bar{\mu}_{3}(\proj{1}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] &  & \ldots\textrm{ etc.}
% \end{aligned}
% \label{eq:Born-QIVPM}
% \end{equation}
% For the same observable~$\mathbf{O}=\proj{0}+2\,\proj{1}+3\,\proj{2}$,
% the only state~$\rho$ consistent with $\bar{\mu}_{3}$ on $\proj{0}$,
% $\proj{1}$, and $\proj{2}$ must be $\proj{\ps}$, and $\mu_{1}=\mu_{\proj{\ps}}^{\mathrm{B}}$.
% Therefore, the expectation value~$\expval{\mathbf{O}}_{\bar{\mu}_{3}}=\left[\expval{\mathbf{O}}_{\mu_{1}},\expval{\mathbf{O}}_{\mu_{1}}\right]=\left[1.5,1.5\right]$
% which is an interval, but not between $0$ and $1$ because it is
% not a probability of an event. 
We also note that, when restricted to commuting projectors,
Eq.~(\ref{eq:quantum-interval-expectation-core}) is consistent with
the classical notion of the \emph{Choquet
  integral}~\citep{Choquet1954,GilboaSchmeidler1994,Grabisch2016}
which is used to calculate the expectation value of random variables
as a weighted average~\citep{HOSTunpublished}.

@@

The expectation value of an observable $\mathbf{O}$ in a Hilbert space
of dimension $d$ relative to a 0-deterministic QIVPM is fully
determinate and is equal to one of the eigenvalues $\lambda_i$ of that
observable. To see this, note that given an orthonormal basis
$\Omega=\{ \ket{\psi_0},\ket{\psi_1},\ldots,\ket{\psi_{d-1}}\}$, a
0-deterministic QIVPM must map exactly one of the projectors
$\proj{\psi_i}$ to $\necess$ and all others to $\imposs$. This is
because, by Eq.~(\ref{eq:necess}), we have
$\bar{\mu}(\Sigma_{j=0}^{d-1}{\proj{\psi_j}})=\necess$ and by inductively
applying Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
we must have one of the $\bar{\mu}(\proj{\psi_i})=\necess$ and all
others mapped to $\imposs$. Given any state~$\rho$ that is consistent
with this QIVPM on all the projectors in $\Omega$, we have by
Eq.~(\ref{eq:hbar}) that $\mu_{\rho}^{\mathrm{B}}$ must also map
exactly one of the projectors in $\Omega$ to 1 and all others to 0. If
an observable has a spectral decomposition along $\Omega$ then, by
Eq.~(\ref{eq:quantum-expectation}), its expectation value relative to
$\mu_{\rho}^{\mathrm{B}}$ is the eigenvalue $\lambda$ whose projector
is mapped to 1. It therefore follows, by
Eq.~(\ref{eq:quantum-interval-expectation-core}), that the expectation
value relative to the 0-deterministic~${\bar{\mu}}$ is fully
determinate and lies in the interval $[\lambda,\lambda]$.

@@

% \begin{table*}
% \caption{\label{tab:Mermin-Peres-Computation}Compute the expectation value
% of of observables~$\ensuremath{\mathbb{1}\otimes\sigma_{z}}$, $\ensuremath{\sigma_{z}\otimes\mathbb{1}}$,
% and $\ensuremath{\sigma_{z}\otimes\sigma_{z}}$ relative to a 0-deterministic
% QIVPM~$\bar{\mu}$. During the computation, whenever $\rho\in\coreBorn\left(\bar{\mu},\events'\right)$,
% $\mu_{\rho}^{\mathrm{B}}\left(P_{1}\right)$ and $\mu_{\rho}^{\mathrm{B}}\left(P_{2}\right)$
% must be the value list in the table. Therefore, $\expval{\mathbf{O}}_{\bar{\mu}}$
% is a singleton set.}
% \begin{tabular}{|c|c|c|c|c|c|c|c|}
% \hline 
% Observable~$\mathbf{O}$ & Spectral Decomposition~$1\cdot P_{1}-1\cdot P_{2}$ & $\bar{\mu}\left(P_{1}\right)$ & $\bar{\mu}\left(P_{2}\right)$ & $\mu_{\rho}^{\mathrm{B}}\left(P_{1}\right)$ & $\mu_{\rho}^{\mathrm{B}}\left(P_{2}\right)$ & $\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}$ & $\expval{\mathbf{O}}_{\bar{\mu}}$\tabularnewline
% \hline 
% \hline 
% $\ensuremath{\mathbb{1}\otimes\sigma_{z}}$ & $1\cdot\left(\proj{0}+\proj{2}\right)-1\cdot\left(\proj{1}+\proj{3}\right)$ & $\imposs$ & $\necess$ & $0$ & $1$ & $1\cdot0-1\cdot1=-1$ & $\left\{ -1\right\} $\tabularnewline
% \hline 
% $\ensuremath{\sigma_{z}\otimes\mathbb{1}}$ & $1\cdot\left(\proj{0}+\proj{1}\right)-1\cdot\left(\proj{2}+\proj{3}\right)$ & $\necess$ & $\imposs$ & $1$ & $0$ & $1\cdot1-1\cdot0=1$ & $\left\{ 1\right\} $\tabularnewline
% \hline 
% $\ensuremath{\sigma_{z}\otimes\sigma_{z}}$ & $1\cdot\left(\proj{0}+\proj{3}\right)-1\cdot\left(\proj{1}+\proj{2}\right)$ & $\imposs$ & $\necess$ & $0$ & $1$ & $1\cdot0-1\cdot1=-1$ & $\left\{ -1\right\} $\tabularnewline
% \hline 
% \end{tabular}
% \end{table*}
% \yutsung{In order to understand the expectation value of observables~$\ensuremath{\mathbb{1}\otimes\sigma_{z}}$,
% $\ensuremath{\sigma_{z}\otimes\mathbb{1}}$, and $\ensuremath{\sigma_{z}\otimes\sigma_{z}}$
% relative to a 0-deterministic QIVPM~$\bar{\mu}$, we first diagonalize
% these observables by the computational basis~$\Omega=\left\{ \ket{0},\ket{1},\ket{2},\ket{3}\right\} $,
% where $\ket{0}=\ket{0}\otimes\ket{0}$, $\ket{1}=\ket{0}\otimes\ket{1}$,
% $\ket{2}=\ket{1}\otimes\ket{0}$, and $\ket{3}=\ket{1}\otimes\ket{1}$.
% Since $\bar{\mu}$ is 0-deterministic, there is a unique $\ket{k_{0}}\in\Omega$
% such that $\bar{\mu}\left(\proj{k_{0}}\right)=\necess$ and $\bar{\mu}\left(\proj{k}\right)=\imposs$
% for $k\ne k_{0}$~\citep{HOSTunpublished}. Without loss of generality,
% assume $k_{0}=1$, the expectation values can be computed step-by-step
% in Table~\ref{tab:Mermin-Peres-Computation}. They are singleton
% sets whose only element is the eigenvalue of the observable. By adopting
% an intuitive product rule~$\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{ x_{0}x_{1}\right\} $
% for singleton sets, these expectation values also satisfy the property~$\expval{\ensuremath{\mathbb{1}\otimes\sigma_{z}}}_{\bar{\mu}}\cdot\expval{\ensuremath{\sigma_{z}\otimes\mathbb{1}}}_{\bar{\mu}}=\expval{\ensuremath{\sigma_{z}\otimes\sigma_{z}}}_{\bar{\mu}}$
% since $\left(\ensuremath{\mathbb{1}\otimes\sigma_{z}}\right)\cdot\left(\ensuremath{\sigma_{z}\otimes\mathbb{1}}\right)=\left(\ensuremath{\sigma_{z}\otimes\sigma_{z}}\right)$.}

@@

\begin{tabular}{cc}
\toprule 
\addlinespace
$P$ & $\bar{\mu}\left(P\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, $\proj{\ps'}$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, 
$\mathbb{1}-\proj{\ps'}$ & $\necess$\tabularnewline\addlinespace
\midrule 
\addlinespace
All other projectors & $\unknown$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}
Next we will prove by contradiction that
$\coreBorn\left(\bar{\mu},\events\right)$ is the empty set. Suppose
there is a state
$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j} > 0$. Since
$\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$ for any~$P$, the
state~$\rho$ must satisfy:
\begin{equation}
\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps'})=0\,,
\end{equation}
which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
for all~$j$. The last equation never holds proving the theorem.

@@

\begin{thm}[Finite-Precision Extension of the Gleason
  Theorem]\label{thm:Finite-precision-Gleason}Let $f$ be a blurring
  function and let $f \circ \mu_{\rho}^{\mathrm{B}}$ be a QIVPM, where
  $\mu_{\rho}^{\mathrm{B}}$ is the probability measure induced by the
  Born rule for a given state $\rho$. Let $\alpha$ be the maximum
  length of intervals in its image. If a state $\rho'$ is consistent
  with $f\circ\mu_{\rho}^{\mathrm{B}}$ on all events, i.e.,
  $\rho'\in\coreBorn\left(f\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
  then the norm of their difference is bounded by $\alpha$, i.e.,
  $\left\Vert \rho-\rho'\right\Vert \le \alpha$.\end{thm}

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{framed}
\newcommand{\amr}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}\end{framed}}
\newcommand{\yutsung}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}\end{framed}}
\newcommand{\gerardo}[1]{\fbox{\begin{minipage}{0.9\linewidth}\color{OliveGreen}{Gerardo says: #1}\end{minipage}}}
\newcommand{\andy}[1]{\fbox{\begin{minipage}{0.9\linewidth}\color{blue}{Andy says: #1}\end{minipage}}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}\mathrel{}\middle|\mathrel{}{#2}\right\} }}
\newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
\allowdisplaybreaks
\newcommand{\coreBorn}{\ensuremath{\overline{\Hilb}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
\setcounter{secnumdepth}{3}
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\rmd}{\mathrm{d}}
\newcommand{\rmi}{\mathrm{i}}
\lineskiplimit=1pt
\newcommand{\ultramodular}{\mathcal{M}}
\newcommand{\ultramodularL}[1][]{\ensuremath{\ultramodular^{\mathrm{L{#1}}}}}
\newcommand{\ultramodularR}[1][]{\ensuremath{\ultramodular^{\mathrm{R{#1}}}}}
\newcommand{\muB}{\ensuremath{\mu^{B}}}

@@

A conventional quantum probability measure can easily be constructed
using the Born rule if one knows the current state of the quantum
system.  Specifically, for each pure normalized quantum
state~$\ket{\phi} \in {\cal H}$, the Born rule induces a probability measure
$\muB_{\phi}$ defined as
$\muB_{\phi}(P)=\melem{\phi}{P}{\phi}$. The situation
generalizes to mixed states
$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, $\ket{\phi_j} \in {\cal H}$, where $q_j > 0$ and
$\sum_{j=1}^{N}q_{j}=1$, in which case the generalized Born rule
induces a probability measure $\muB_{\rho}$ defined as
$\muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) =
\sum_{j=1}^{N}
q_{j}\muB_{\phi_{j}}\left(P\right)$~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.

@@

In the remainder of this section, we will show that our definition of
QIVPMs is consistent with classical IVPMs in the sense that a
restriction of QIVPMs to commuting events recovers the definition of
classical IVPMs. To formalize this connection between QIVPMs and
classical IVPMs, we first note that in contrast to the case with
conventional quantum probability spaces, there is generally no unique
state~$\rho$ consistent with a QIVPM. We say that a QIVPM $\bar{\mu}$
is consistent with a state $\rho$ and projector~$P$ if the interval
$\bar{\mu}(P)$ contains the exact probability calculated by the Born
rule, i.e, if:
\begin{equation}
\muB_{\rho}\left(P\right)\in\bar{\mu}\left(P\right)
\end{equation}
where $\muB_{\rho}\left(P\right)=\Tr\left(\rho P\right)$
is the probability of the event~$P$ as determined by the Born
rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.

We generalize this consistency relation to sets of states and general
subspaces of events as follows. A set of events $\events'$ is a
\emph{subspace} of $\events$ if it contains $\mathbb{0}$
and~$\mathbb{1}$ and is closed under complements, sums, and products,
i.e., for any projector~$P\in\events'$, we have
$\mathbb{1}-P\in\events'$ and for each pair of commuting
projectors~$P_{0}\in\events'$ and $P_{1}\in\events'$, we have
$P_{0}+P_{1}-P_{0}P_{1}$ and $P_{0}P_{1}\in\events'$. Given a
probability measure $\bar{\mu}$ and a subspace of events $\events'$,
we denote the collection of all states that are consistent with
$\bar{\mu}$ on every projector in $\events'$ as
$\coreBorn(\bar{\mu},\events')$:
\begin{equation}
\label{eq:hbar}
\coreBorn\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in \events',~\muB_{\rho}\left(P\right)\in\bar{\mu}\left(P\right)}.
\end{equation}

@@

\begin{definition}[Expectation Value of Observables over QIVPMs] Let
  $\mathscr{I}$ be a set of intervals; $\Hilb$ a Hilbert space of
  dimension $d$ with event space~$\events$; and $\mathbf{O}$ an
  observable with spectral decomposition
  $\Sigma_{i=1}^d \lambda_iP_i$. Let $\events'$ be the minimal
  subspace of events containing all the projectors $P_i$ in the
  spectral decomposition of $\mathbf{O}$ and define:
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}
\expval{\mathbf{O}}_{\muB_{\rho}},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}
\expval{\mathbf{O}}_{\muB_{\rho}}\right]\,. \label{eq:quantum-interval-expectation-core}
\end{equation}
\end{definition}

\noindent Intuitively the expectation value of an observable relative
to a QIVPM $\bar{\mu}$ lies between two possible outcomes, which
themselves lie between the minimum and maximum bounds of the
probability intervals associated with each state~$\rho$ that is
consistent with~$\bar{\mu}$ on every projector in the spectral
decomposition of the observable. If $\bar{\mu}$ is a conventional
(Born) probability measure induced by a state $\rho$, then the Born
rule probability induced by every state in
$\coreBorn\left(\bar{\mu},\events'\right)$ will be
$\muB_{\rho}$ and the interval collapses to a point, thus
reducing the definition to that of
Eq.~(\ref{eq:quantum-expectation})~\citep{HOSTunpublished}.
% For example, we can extend one of the fragments of valid probability
% measures~$\mu_{1}$ defined in Table~\ref{tab:quantum-probability-measure}
% to a QIVPM~$\bar{\mu}_{3}$:
% \begin{equation}
% \begin{aligned}\bar{\mu}_{3}(\proj{0}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] & \bar{\mu}_{3}(\proj{2}) & =\left[0,0\right]\\
% \bar{\mu}_{3}(\proj{1}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] &  & \ldots\textrm{ etc.}
% \end{aligned}
% \label{eq:Born-QIVPM}
% \end{equation}
% For the same observable~$\mathbf{O}=\proj{0}+2\,\proj{1}+3\,\proj{2}$,
% the only state~$\rho$ consistent with $\bar{\mu}_{3}$ on $\proj{0}$,
% $\proj{1}$, and $\proj{2}$ must be $\proj{\ps}$, and $\mu_{1}=\muB_{\proj{\ps}}$.
% Therefore, the expectation value~$\expval{\mathbf{O}}_{\bar{\mu}_{3}}=\left[\expval{\mathbf{O}}_{\mu_{1}},\expval{\mathbf{O}}_{\mu_{1}}\right]=\left[1.5,1.5\right]$
% which is an interval, but not between $0$ and $1$ because it is
% not a probability of an event. 
We also note that, when restricted to commuting projectors,
Eq.~(\ref{eq:quantum-interval-expectation-core}) is consistent with
the classical notion of the \emph{Choquet
  integral}~\citep{Choquet1954,GilboaSchmeidler1994,Grabisch2016}
which is used to calculate the expectation value of random variables
as a weighted average~\citep{HOSTunpublished}.

@@

The expectation value of an observable $\mathbf{O}$ in a Hilbert space
of dimension $d$ relative to a 0-deterministic QIVPM is fully
determinate and is equal to one of the eigenvalues $\lambda_i$ of that
observable. To see this, note that given an orthonormal basis
$\Omega=\{ \ket{\psi_0},\ket{\psi_1},\ldots,\ket{\psi_{d-1}}\}$, a
0-deterministic QIVPM must map exactly one of the projectors
$\proj{\psi_i}$ to $\necess$ and all others to $\imposs$. This is
because, by Eq.~(\ref{eq:necess}), we have
$\bar{\mu}(\Sigma_{j=0}^{d-1}{\proj{\psi_j}})=\necess$ and by inductively
applying Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
we must have one of the $\bar{\mu}(\proj{\psi_i})=\necess$ and all
others mapped to $\imposs$. Given any state~$\rho$ that is consistent
with this QIVPM on all the projectors in $\Omega$, we have by
Eq.~(\ref{eq:hbar}) that $\muB_{\rho}$ must also map
exactly one of the projectors in $\Omega$ to 1 and all others to 0. If
an observable has a spectral decomposition along $\Omega$ then, by
Eq.~(\ref{eq:quantum-expectation}), its expectation value relative to
$\muB_{\rho}$ is the eigenvalue $\lambda$ whose projector
is mapped to 1. It therefore follows, by
Eq.~(\ref{eq:quantum-interval-expectation-core}), that the expectation
value relative to the 0-deterministic~${\bar{\mu}}$ is fully
determinate and lies in the interval $[\lambda,\lambda]$.

@@

% \begin{table*}
% \caption{\label{tab:Mermin-Peres-Computation}Compute the expectation value
% of of observables~$\ensuremath{\mathbb{1}\otimes\sigma_{z}}$, $\ensuremath{\sigma_{z}\otimes\mathbb{1}}$,
% and $\ensuremath{\sigma_{z}\otimes\sigma_{z}}$ relative to a 0-deterministic
% QIVPM~$\bar{\mu}$. During the computation, whenever $\rho\in\coreBorn\left(\bar{\mu},\events'\right)$,
% $\muB_{\rho}\left(P_{1}\right)$ and $\muB_{\rho}\left(P_{2}\right)$
% must be the value list in the table. Therefore, $\expval{\mathbf{O}}_{\bar{\mu}}$
% is a singleton set.}
% \begin{tabular}{|c|c|c|c|c|c|c|c|}
% \hline 
% Observable~$\mathbf{O}$ & Spectral Decomposition~$1\cdot P_{1}-1\cdot P_{2}$ & $\bar{\mu}\left(P_{1}\right)$ & $\bar{\mu}\left(P_{2}\right)$ & $\muB_{\rho}\left(P_{1}\right)$ & $\muB_{\rho}\left(P_{2}\right)$ & $\expval{\mathbf{O}}_{\muB_{\rho}}$ & $\expval{\mathbf{O}}_{\bar{\mu}}$\tabularnewline
% \hline 
% \hline 
% $\ensuremath{\mathbb{1}\otimes\sigma_{z}}$ & $1\cdot\left(\proj{0}+\proj{2}\right)-1\cdot\left(\proj{1}+\proj{3}\right)$ & $\imposs$ & $\necess$ & $0$ & $1$ & $1\cdot0-1\cdot1=-1$ & $\left\{ -1\right\} $\tabularnewline
% \hline 
% $\ensuremath{\sigma_{z}\otimes\mathbb{1}}$ & $1\cdot\left(\proj{0}+\proj{1}\right)-1\cdot\left(\proj{2}+\proj{3}\right)$ & $\necess$ & $\imposs$ & $1$ & $0$ & $1\cdot1-1\cdot0=1$ & $\left\{ 1\right\} $\tabularnewline
% \hline 
% $\ensuremath{\sigma_{z}\otimes\sigma_{z}}$ & $1\cdot\left(\proj{0}+\proj{3}\right)-1\cdot\left(\proj{1}+\proj{2}\right)$ & $\imposs$ & $\necess$ & $0$ & $1$ & $1\cdot0-1\cdot1=-1$ & $\left\{ -1\right\} $\tabularnewline
% \hline 
% \end{tabular}
% \end{table*}
% \yutsung{In order to understand the expectation value of observables~$\ensuremath{\mathbb{1}\otimes\sigma_{z}}$,
% $\ensuremath{\sigma_{z}\otimes\mathbb{1}}$, and $\ensuremath{\sigma_{z}\otimes\sigma_{z}}$
% relative to a 0-deterministic QIVPM~$\bar{\mu}$, we first diagonalize
% these observables by the computational basis~$\Omega=\left\{ \ket{0},\ket{1},\ket{2},\ket{3}\right\} $,
% where $\ket{0}=\ket{0}\otimes\ket{0}$, $\ket{1}=\ket{0}\otimes\ket{1}$,
% $\ket{2}=\ket{1}\otimes\ket{0}$, and $\ket{3}=\ket{1}\otimes\ket{1}$.
% Since $\bar{\mu}$ is 0-deterministic, there is a unique $\ket{k_{0}}\in\Omega$
% such that $\bar{\mu}\left(\proj{k_{0}}\right)=\necess$ and $\bar{\mu}\left(\proj{k}\right)=\imposs$
% for $k\ne k_{0}$~\citep{HOSTunpublished}. Without loss of generality,
% assume $k_{0}=1$, the expectation values can be computed step-by-step
% in Table~\ref{tab:Mermin-Peres-Computation}. They are singleton
% sets whose only element is the eigenvalue of the observable. By adopting
% an intuitive product rule~$\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{ x_{0}x_{1}\right\} $
% for singleton sets, these expectation values also satisfy the property~$\expval{\ensuremath{\mathbb{1}\otimes\sigma_{z}}}_{\bar{\mu}}\cdot\expval{\ensuremath{\sigma_{z}\otimes\mathbb{1}}}_{\bar{\mu}}=\expval{\ensuremath{\sigma_{z}\otimes\sigma_{z}}}_{\bar{\mu}}$
% since $\left(\ensuremath{\mathbb{1}\otimes\sigma_{z}}\right)\cdot\left(\ensuremath{\sigma_{z}\otimes\mathbb{1}}\right)=\left(\ensuremath{\sigma_{z}\otimes\sigma_{z}}\right)$.}

@@

\begin{tabular}{cc}
\toprule 
\addlinespace
$P$ & $\bar{\mu}\left(P\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, $\proj{\ps'}$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, 
$\mathbb{1}-\proj{\ps'}$ & $\necess$\tabularnewline\addlinespace
\midrule 
\addlinespace
All other projectors & $\unknown$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}
Next we will prove by contradiction that
$\coreBorn\left(\bar{\mu},\events\right)$ is the empty set. Suppose
there is a state
$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j} > 0$. Since
$\muB_{\rho}(P)\in\bar{\mu}(P)$ for any~$P$, the
state~$\rho$ must satisfy:
\begin{equation}
\muB_{\rho}(\proj{0})=\muB_{\rho}(\proj{\ps})=\muB_{\rho}(\proj{\ps'})=0\,,
\end{equation}
which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
for all~$j$. The last equation never holds proving the theorem.

@@

\begin{thm}[Finite-Precision Extension of the Gleason
  Theorem]\label{thm:Finite-precision-Gleason}Let $f$ be a blurring
  function and let $f \circ \muB_{\rho}$ be a QIVPM, where
  $\muB_{\rho}$ is the probability measure induced by the
  Born rule for a given state $\rho$. Let $\alpha$ be the maximum
  length of intervals in its image. If a state $\rho'$ is consistent
  with $f\circ\muB_{\rho}$ on all events, i.e.,
  $\rho'\in\coreBorn\left(f\circ\muB_{\rho},\events\right)$,
  then the norm of their difference is bounded by $\alpha$, i.e.,
  $\left\Vert \rho-\rho'\right\Vert \le \alpha$.\end{thm}

The proof proceeds as follows. Given a state~$\rho'$ consistent with
$f\circ\muB_{\rho}$, we have
$\muB_{\rho'}\left(\proj{\psi}\right)\in
f\left(\muB_{\rho}\left(\proj{\psi}\right)\right)$ for any
one-dimensional projector $P=\proj{\psi}$. Since the maximum length of
the intervals in $\mathscr{I}$ is $\alpha$, it is also the upper bound
of the difference:
\[
\left|\muB_{\rho'}\left(\proj{\psi}\right)-\muB_{\rho}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|\le \alpha\,.
\]
Since $\rho-\rho'$ is Hermitian, $\max_{\left\Vert \psi\right\Vert =1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$
is the maximum absolute value of the eigenvalues of $\rho-\rho'$~\citep{544199},
and equal to $\left\Vert \rho-\rho'\right\Vert $~\citep{GolubVanLoan1996,Foucart2012}.
Hence, $\left\Vert \rho-\rho'\right\Vert \le \alpha$.
